CrystalPlan: an Experiment Planning Tool for Crystallography

### 2010-12-16 docs/CrystalPlan_paper/paper.tex
Refs #182. All Pete's comments are in.

\newif\ifdograph
% \dographtrue % DO keep the graphs.
\dographfalse % DONT put graphs - makes things faster

@@

\cauthor[a]{Janik}{Zikovsky}{zikovskyjl@ornl.gov}{address if different from
\aff}
\author[a]{Peter}{Peterson}
\author[a]{Xiaoping}{Wang}
\author[a]{Matthew}{Frost}
\author[a]{Christina}{Hoffmann}

\aff[a]{Spallation Neutron Source, Oak Ridge National Laboratory, P.O. Box 2008
MS-6477, Oak Ridge, TN 37831-6477
\country{USA}}

@@

\begin{figure}
\caption{GUI showing details of the predicted measurement positions for a
single $hkl$.}
\ifdograph
  \includegraphics[width=2.5in]{single_reflection_3}
\fi

>>>>

\newif\ifdograph
\dographtrue % DO keep the graphs.
%\dographfalse % DONT put graphs - makes things faster

@@

\cauthor[]{Janik}{Zikovsky}{zikovskyjl@ornl.gov}{address if different from
\aff}
\author[]{Peter}{Peterson}
\author[]{Xiaoping}{Wang}
\author[]{Matthew}{Frost}
\author[]{Christina}{Hoffmann}

\aff[]{Spallation Neutron Source, Oak Ridge National Laboratory, P.O. Box 2008
MS-6477, Oak Ridge, TN 37831-6477
\country{USA}}

@@

\begin{figure}
\caption{GUI showing details of the predicted measurement positions for a
single $hkl$.}
\ifdograph
  \includegraphics[width=3in]{single_reflection_3}
\fi
